Long_time_series

### 2019-04-27 Exploring/Detect_MCSs.Rmd
updating

ts <- ts2clm(MUR_SST_PN, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_MUR_PN <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_PN")

MUR_SST_LB <- MUR_SST %>% 
  filter(site == "Lamberts Bay") %>% 
  dplyr::rename(temp = nearest1) %>% 
  select(date, temp) %>% 
  dplyr::rename(t = date)

>>>>

ts <- ts2clm(MUR_SST_PN, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_MUR_PN <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_PN") 
library(tidyverse)
library(heatwaveR)
MUR_SST_LB <- MUR_SST %>% 
  filter(site == "Lamberts Bay") %>% 
  dplyr::rename(temp = nearest1) %>% 
  select(date, temp) %>% 
  dplyr::rename(t = date)
